HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-08 scnn.tex
small update

    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
    \item (done!) (NP) make figure A.13 remove white space
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network is
\begin{equation*}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation*}
where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

>>>>

    \item (MD+NP) talk about the loss in 3.8 (old 4.8) \nati{I was very brief. In color for now.}
    \item (done!) (NP) make figure A.13 remove white space
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network is
\begin{equation*}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation*}
where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
\todo{For a regression task, the most common choice is the $L^2$ norm $\ell(\y) = \|\y-\bar{\y}\|_2^2$, where $\bar{\y}$ is the desired output, as it minimize the mean square error. We emphasis that by sole change of the loss, one can solve regularization instead of classification.}

The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
